Improving phase-matching of FWM with temperature

### 2015-09-21 latex/article.tex
images and problems

@@

\begin{subequations}
\begin{align}
	\frac{\partial^2F(x,y)}{\partial x^2} + \frac{\partial^2F(x,y)}{\partial y^2} + \left[ k_0^2n^2(x,y)-\beta^2\right]F(x,y) = 0
	\label{eq_wg_a} \\
	\frac{\partial^2\tilde{A}(z,\omega)}{\partial z^2} +2\mathrm{i}\beta\frac{\partial \tilde{A}(z,\omega)}{\partial z} +3n^2k_0^2\tilde{A}(z,\omega) = 0
	\quad ! \neq ! \quad
	2\mathrm{i}\beta_0\frac{\partial \tilde{A}(z,\omega)}{\partial z} +(\tilde{\beta}^2 - \beta_0^2)\tilde{A}(z,\omega) = 0
	\label{eq_wg_b}
\end{align}
\end{subequations}
where $k_0$ is the wavevector in vacuum and $n=n(x,y)$ is a function of the position (mainly $x$ and $y$ for a straight waveguide).

@@

The second equation (\ref{eq_wg_b}), on the other hand, define the change of field distribution along the $\hat{z}$ axis, or the waveguide axis.
Imposing to this equation to be zero means that we force the field distribution $F$ not to change.
Indeed not all field distributions are transmitted through the waveguide without energy loss \textbf{(?)} and thus without changing $F$.
% Modes are fields that maintain the same transverse distribution and polarization at all locations along the waveguide axis.
Those field distributions which maintain the same transverse distribution and polarization at all locations along the waveguide axis are called modes.
These modes can be categorized in two main groups, depending on the polarization of the wave: transverse electric (TE) modes and transverse magnetic (TM) modes, which have respectively the electric and magnetic field transverse to the waveguide axis.

@@

\subsection{Data processing}

@@

We obtained graphs representing the position and the bandwidth of peaks vs temperature of each solution, as shown if Figure (\ref{fig_examples}).

\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=1\textwidth]{ex_pos.png}
		\caption{Example of peaks vs $T_H$.}
		\label{fig_example_position}
	\end{subfigure}\hspace{.05\textwidth}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=1\textwidth]{ex_bw.png}
		\caption{Example of bandwidth vs $T_H$.}
		\label{fig_example_bandwidth}
	\end{subfigure}
	\caption{Examples of peaks position and bandwidth dependence on temperature $T_H$}
	\label{fig_examples}
\end{figure}

@@

The next Figures (\ref{fig_sym_pp}) and (\ref{fig_sym_bw}) show the results obtained, excluding the sets which only phasematch was at $\lambda = \SI{1.55}{\um}$

>>>>

\usepackage{svg}			% to include svgs

@@

\begin{subequations}
\begin{align}
	\frac{\partial^2F(x,y)}{\partial x^2} + \frac{\partial^2F(x,y)}{\partial y^2} + \left[ k_0^2n^2(x,y)-\beta^2\right]F(x,y) = 0
	\label{eq_wg_a} \\
	\frac{\partial^2\tilde{A}(z,\omega)}{\partial z^2} +2\mathrm{i}\beta\frac{\partial \tilde{A}(z,\omega)}{\partial z} -n^2k_0^2\tilde{A}(z,\omega) = 0
	\quad ! \neq ! \quad
	2\mathrm{i}\beta_0\frac{\partial \tilde{A}(z,\omega)}{\partial z} +(\tilde{\beta}^2 - \beta_0^2)\tilde{A}(z,\omega) = 0
	\label{eq_wg_b}
\end{align}
\end{subequations}
where $k_0$ is the wavevector in vacuum and $n=n(x,y)$ is a function of the position (mainly $x$ and $y$ for a straight waveguide).

@@

The second equation (\ref{eq_wg_b}), on the other hand, defines the change of field distribution along the $\hat{z}$ axis, or the waveguide axis.
Imposing to this equation to be zero means that we force the field distribution $F$ not to change.
Indeed not all field distributions are transmitted through the waveguide without energy loss \textbf{(?)} and thus without changing $F$.
% Modes are fields that maintain the same transverse distribution and polarization at all locations along the waveguide axis.
Those field distributions which maintain the same transverse distribution and polarization at all locations along the waveguide axis are called modes.
These modes can be categorized in two main groups, depending on the polarization of the wave: transverse electric (TE) modes and transverse magnetic (TM) modes, which have respectively the electric and magnetic field transverse to the waveguide axis.

@@

\subsection{Data processing}
We focused on the information given by the effective index.

@@

We obtained graphs representing the position and the bandwidth of peaks vs temperature of each solution, as shown in Figures (\ref{fig_example_position}) and (\ref{fig_example_bandwidth}).

\begin{figure}[!h]
	\centering
	\includegraphics[width=.75\textwidth]{ex_pos.png}
	\caption{Example of peaks vs $T_H$.}
	\label{fig_example_position}
\end{figure}
\begin{figure}[!h]
	\centering
%	\includegraphics[scale=1]{ex_bw.png}
	\includegraphics[width=.75\textwidth]{ex_bw.png}
	\caption{Example of bandwidth vs $T_H$.}
	\label{fig_example_bandwidth}
\end{figure}

%\begin{figure}[!h]
%	\centering
%	\begin{subfigure}[b]{0.45\textwidth}
%		\includegraphics[width=1\textwidth]{ex_pos.png}
%		\caption{Example of peaks vs $T_H$.}
%		\label{fig_example_position}
%	\end{subfigure}%\hspace{.02\textwidth}
%	\begin{subfigure}[b]{0.45\textwidth}
%		\includegraphics[width=1\textwidth]{ex_bw.png}
%		\caption{Example of bandwidth vs $T_H$.}
%		\label{fig_example_bandwidth}
%	\end{subfigure}
%	\caption{Examples of peaks position and bandwidth dependence on temperature $T_H$}
%	\label{fig_examples}
%\end{figure}

@@

%The next Figures (\ref{fig_sym_pp}) and (\ref{fig_sym_bw}) show the results obtained, excluding the sets which only phasematch was at $\lambda = \SI{1.55}{\um}$
